Child care situation of working mothers in Ghana 1998

### 2022-04-03 outputs/paper.Rmd
Appendix
Update paper

```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the child caretaker for working mothers", fig.width=6, fig.height=4}
totl <-
  ghana %>%
  filter(character=="Total") %>%
  mutate(
    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
  )
# make dataset in long format
totl_long <-
  totl %>%
  select(-c(character, total, caretaker_missing)) %>%
  pivot_longer(!background, names_to = "variable", values_to = "count")

@@

# Appendix

>>>>

```{r generalchildcare, echo=FALSE, fig.cap="Distribution of the caretaker for working mothers", fig.width=6, fig.height=4}
totl <-
  ghana %>%
  filter(character=="Total") %>%
  mutate(
    no_child_under_six = round(no_child_under_six/100 * number_of_employed_women, 0),
    one_more_child_under_six = round(one_more_child_under_six/100 * number_of_employed_women, 0)
  )
# make dataset in long format
totl_long <-
  totl %>%
  select(-c(character, total, caretaker_missing)) %>%
  pivot_longer(!background, names_to = "variable", values_to = "count")

@@

# (APPENDIX) Appendix {-}

# Datasheet
